Modelling BCG vaccination in the UK

### 2019-05-03 index/08-model-development.Rmd
dropped unneccessary modelling dep
Former-commit-id: 13926ebe3fdae9da7f71e85c19204c72d4168a9b
Former-commit-id: fc5333abe590a8969b5a7a11a2742116be679ef8

## Wordcount: 10220
##packages
library(tidyverse)
library(ModelTBBCGEngland)
library(kableExtra)
library(pander)
## Resources path
resources_path <- file.path("chapters", "model-development")
```

>>>>

## Wordcount: 10220
##packages
library(tidyverse)
library(kableExtra)
library(pander)
## Resources path
resources_path <- file.path("chapters", "model-development")

## Read data: https://github.com/seabbs/ModelTBBCGEngland/data
load_formated <- function(name) {

  path <- file.path("chapters/model-development/data", paste0(name, ".rda"))

  load(path, envir = globalenv())
}

load_formated("disease_params_table")
load_formated("demographic_params_table")
load_formated("sources_table")
load_formated("eff_bcg")
```

### 2019-05-03 index/09-model-fitting.Rmd
dropped unneccessary modelling dep
Former-commit-id: 13926ebe3fdae9da7f71e85c19204c72d4168a9b
Former-commit-id: fc5333abe590a8969b5a7a11a2742116be679ef8

## Wordcount: 5501
##packages
library(tidyverse)
library(ModelTBBCGEngland)
library(kableExtra)
library(pander)
## Resources path
resources_path <- file.path("chapters", "model_fitting")
```

>>>>

## Wordcount: 5501
##packages
library(tidyverse)
library(kableExtra)
library(pander)
## Resources path
resources_path <- file.path("chapters", "model_fitting")

## Read data: https://github.com/seabbs/ModelTBBCGEngland/data
load_formated <- function(name) {

  path <- file.path("chapters/model-development/data", paste0(name, ".rda"))

  load(path, envir = globalenv())
}

load_formated("measurement_params_table")
```
